Ceph Parallel File System Evaluation Report

### 2013-08-23 introduction.tex
update introduction section

National Center for Computational Sciences (NCCS), in collaboration with
Inktank Inc, prepared this performance and scalability study of
Ceph file system. Ceph originated from Sage Weil's PhD research
at UC Santa Cruz around 2007 and it was designed to be a reliable, scalable
fault-tolerant parallel file system. Inktank is now the major developer behind
the open-source parallel file system to sheperd its development and provide
commercial support.

In comparison to other parallel file systems, Ceph has a number of distinctive
features:

@@

\item Ceph is built on top of a unified object management layer,
\texttt{RADOS}. Both metadata and the file data can take advantage of this
uniformity.

@@

As part of this effort, we set up a dedicated testbed within NCCS for the Ceph
file system evaluation. The goal of our study is to investigate the
feasibility of using the Ceph for our future HPC storage deployment.  This
report presents our experience, results, and observations. While evaluating
our results, please keep in mind that Ceph is still a relatively
\textit{young} parallel file system and its code base is changing rapidly. In
between releases, we often experienced different stability and performance
outcomes.  We will try to make clear in the report when such changes occurred.

>>>>

National Center for Computational Sciences (NCCS) runs one of the largest HPC
storage system built on top of Lustre parallel file system. The latest
installation of Spider II is designed to operate at over 1 TB/s peak
throughput with 40 PB of raw capacity. As a scratch file system connected to a
leadership computing platform at the scale of Titan, Spider II emphasizes
\textit{capability} over \textit{capacity}. However, we also recognize that
there are a wide variety of scientific data and workloads with different
performance and data access requirements, e.g., RESTful interface, S3-like
API, cloud solution integration, to name a few.

Ceph\cite{Weil:2006:Ceph} originated from Sage Weil's PhD research at UC Santa
Cruz at 2007 and it was designed to be a reliable, scalable fault-tolerant
parallel file system.  Inktank is now the major developer behind the
open-source parallel file system to shepherd its development and provide
commercial support.  In comparison to other parallel file systems, Ceph has a
number of distinctive features:

@@

  \item Ceph is built on top of a unified object management layer, RADOS. Both
  metadata and the file data can take advantage of this uniformity. On top of
  RADOS, Ceph build and project a host of other features such as RESTful
  interface, S3 and Swift-compliant API, cloud integration.

@@

As interesting and feature-rich as Ceph may be, our environment and the sheer
scale of its potential application drive us to first look into its scalability
and performance.  As part of the study, we set up a dedicated testbed within
NCCS for the Ceph file system evaluation. The goal of our study is to
investigate the feasibility of using the Ceph for our future HPC storage
deployment. This paper presents our experience, results, and observations.
While evaluating our results, please keep in mind that Ceph is still a
relatively \textit{young} parallel file system and its code base is changing
rapidly. In between releases, we often experienced different stability and
performance outcomes.  We will try to make clear in the writing when such
changes occurred.

This paper is organized as follows. Section~\ref{sec:testbed} gives an
overview on our general test and evaluation methodology as well as testbed
environment; Following it, Section~\ref{sec:baseline} establishes the baseline
performance and expectations for all critical components on the data path;
Section~\ref{sec:ceph-initial} discusses our early runs, results, and issues
bottom up: from middle tier RADOS object layer to the file system-level and
then metadata performance. In Section~\ref{sec:ceph-tuning} we highlight the
investigative and tuning effort, we compare results before and after, and how
the process eventually bring the system performance to a respectable state.
Finally, Section~\ref{sec:conclusion} summarizes our findings, observations,
and future works.
